Handwritten Digit Recognition Using Deep Convolutional Neural Network*

### 2022-04-19 paper/paper.tex
paper structure updated and README added
changed layout to IEEE conference paper

\documentclass[11pt]{article}
\usepackage[a4paper, total={6.8in, 10.2in}]{geometry}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage[symbol]{footmisc}
\usepackage{apacite}

\usepackage[hidelinks]{hyperref}
\hypersetup{
    bookmarksopen=true
}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand\bibliographytypesize{\scriptsize}

\title{Handwritten Digit Recognition Using Deep Convolutional Neural Network\footnotemark}
\author{Ammar Elsabe \hfill{} U19100452\\
        Mohamed Alzaabi \hfill{} U17105281\\
        Abdulaziz Abdullatif \hfill{} U18103708\\
}

\date{}

@@

\twocolumn[{%
    \begin{@twocolumnfalse}
        \maketitle
        \begin{abstract}
            \blindtext
        \end{abstract}
    \end{@twocolumnfalse}
}]

\section{Introduction}
\footnotetext[1]{Code can be found at \url{github.com/ammar-elsabe/handwritten-digit-recognition-using-deep-learning.git}}
\Blindtext

\section{Applications of CNNs}
\Blindtext

@@

\bibliographystyle{apacite}
\bibliography{paper.bib}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{graphicx}

\usepackage[hidelinks]{hyperref}
\hypersetup{
    bookmarksopen=true,
}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

@@

\title{Handwritten Digit Recognition Using Deep Convolutional Neural Network*}

\author{\IEEEauthorblockN{Ammar Elsabe}
\IEEEauthorblockA{
    U19100452@sharjah.ac.ae\\
    University ID: U19100452
}

\and

\IEEEauthorblockN{Mohamed Alzaabi}
\IEEEauthorblockA{
    U17105281@sharjah.ac.ae\\
    University ID: U17105281
}

\and

\IEEEauthorblockN{Abdulaziz Abdullatif}
\IEEEauthorblockA{
    U18103708@sharjah.ac.ae\\
    University ID: U18103708
}}

\maketitle
\begin{abstract}
    \blindtext
\end{abstract}

\section{Introduction}
\footnotetext[1]{Code can be found at \href{github.com/ammar-elsabe/handwritten-digit-recognition-DCNN.git}{\texttt{github.com/ammar-elsabe/handwritten-\\digit-recognition-DCNN.git}}}
\Blindtext

\section{CNNs And Their Applications}
\Blindtext

\section{The MNIST Dataset}
\Blindtext

@@

%\bibliographystyle{IEEEtran}
%\bibliography{paper.bib}
